---
title: "{{cookiecutter.project_name}}"
subtitle: "By {{cookiecutter.name}} ({{cookiecutter.email}}) `r Sys.Date()`"
output: powerpoint_presentation
date: "`r Sys.Date()`"
params:
  fig_width: 12
  fig_height: 8
---

```{r setup, include=FALSE}
library(tidyverse)
theme_set(theme_bw())
knitr::opts_chunk$set(echo = FALSE)
knitr::opts_chunk$set(cache = FALSE)
```

## {{cookiecutter.project_name}}

{{cookiecutter.project_short_description}}

## R Markdown

This is an R Markdown presentation. Markdown is a simple formatting syntax for authoring HTML, PDF, and MS Word documents. For more details on using R Markdown see <http://rmarkdown.rstudio.com>.

When you click the **Knit** button a document will be generated that includes both content as well as the output of any embedded R code chunks within the document.

## Useful docs

* [Rendering PowerPoint Presentations with the RStudio IDE](https://support.posit.co/hc/en-us/articles/360004672913-Rendering-PowerPoint-Presentations-with-the-RStudio-IDE)
* [R Markdown section on PowerPoint presentations](https://bookdown.org/yihui/rmarkdown/powerpoint-presentation.html)

## Markdown to slides

Pandoc determines the slide level, the markdown document is carved up into slides according the the following rules:

* Headers at the slide level always starts a new slide
* Headers above the slide level in the hierarchy create section headers
* Headers below the slide level in the hierarchy create headers within a slide
* A horizontal rule always starts a new slide
* A title page is constructed automatically from the document’s title (i.e. YAML) block

## Markdown features

*italic* 
**bold** 
~~strikeout~~ 
~subscript~
^superscript^
[small caps]{.smallcaps} 
`verbatim`

1. Numbered list
* Unnumbered list

$math-expression$
$$math-equation$$

[link](target) 

> Block quotations

## Table

 manufacturer    displ   hwy     class
-------------    ------  -----  ---------
        audi     1.8     29      compact
   chevrolet     5.3     20        suv
       dodge     2.4     24      minivan
       
Table: Simple table syntax and caption.
       
## Table 2 (using different Markdown)

| manufacturer  | displ  | hwy   | class     |
| ------------: | :----- | :---- | :-------: |
|        audi   |   1.8  |  29   | compact   |
|   chevrolet   |   5.3  |  20   | suv       |
|       dodge   |   2.4  |  24   | minivan   |

Table: Simple table syntax and caption.

## Two content layout

:::::::::::::: {.columns}
::: {.column}
one
:::
::: {.column}
two
:::
::::::::::::::

## Speaker notes

My slide.

::: notes
This is a speaker note.

- Use basic Markdown
- like this list
- *and inline formatting*
:::

## Slide with R Output

```{r cars, echo = TRUE}
summary(cars)
```

## Slide with Plot

```{r pressure, fig.width=params$fig_width, fig.height=params$fig_height}
plot(pressure)
```
